EDIpack: A generic and interoperable Lanczos-based solver for quantum impurity problems

### 2025-06-01 01_intro.tex
Updated Bibliobraphy with correct naming conventions <Author><Year><JournalAcronym>[a-z]

Most notably, quantum impurity problems lie at the core of many quantum embedding methods, like dynamical mean-field theory (DMFT)~\cite{Georges1996RMP}, density-matrix embedding theory (DMET)~\cite{Knizia2012_DMET} and Gutzwiller approximation (GA)~\cite{Lanata2015_GA}, where the complex behavior of the lattice systems is reduced to an effective self-consistent quantum impurity problem. The present code has been developed with a particular focus for DMFT but its usage extends also to the aforementioned methods.
}
By accounting for local quantum fluctuations, DMFT can successfully describe the most important physical features of correlated materials, including Mott insulators, heavy fermion compounds, and high-temperature superconductors.

Accurately and efficiently solving a quantum impurity problem and computing the Green's functions, which are central in the DMFT framework, remains a
critical challenge, particularly for multi-orbital systems, systems
at low temperatures or endowed with lower symmetry. During many years of development, different advanced numerical techniques have been developed together with cutting edge approaches aimed to reduce computational load. 
\fixme{(Samuele) Numerous exact diagonalization (ED) open-source software packages have been developed by the scientific community addressing the quantum many-body problem, with a strong emphasis on both efficiency and flexibility. Notably, these include codes designed for general systems of interacting fermions, such as EDLib~\cite{Iskakov2017_EDLib} and the more recent XDiag~\cite{wietek2025_xdiag}; for systems involving both fermions and bosons, such as Pomerol~\cite{Antipov2015_pomerol}; and for fermions coupled with spins, such as H$\Phi$~\cite{KAWAMURA2017_Hphi,Ido2024_Hphiupdate}.

>>>>

Most notably, quantum impurity problems lie at the core of many quantum embedding methods, like dynamical mean-field theory (DMFT)~\cite{Georges1996RMP}, density-matrix embedding theory (DMET)~\cite{Knizia2012PRL} and the Gutzwiller approximation (GA)~\cite{Lanata2015PRX}, where the complex behavior of the lattice systems is reduced to an effective self-consistent quantum impurity problem. The present code has been developed with a particular focus for DMFT but its usage extends also to the aforementioned methods.
}
By accounting for local quantum fluctuations, DMFT can successfully describe the most important physical features of correlated materials, including Mott insulators, heavy fermion compounds, and high-temperature superconductors.

Accurately and efficiently solving a quantum impurity problem and computing the Green's functions, which are central in the DMFT framework, remains a
critical challenge, particularly for multi-orbital systems, systems
at low temperatures or endowed with lower symmetry. During many years of development, different advanced numerical techniques have been developed together with cutting edge approaches aimed to reduce computational load. 
\fixme{(Samuele) Numerous exact diagonalization (ED) open-source software packages have been developed by the scientific community addressing the quantum many-body problem, with a strong emphasis on both efficiency and flexibility. Notably, these include codes designed for general systems of interacting fermions, such as EDLib~\cite{Iskakov2017} and the more recent XDiag~\cite{Wietek2025}; for systems involving both fermions and bosons, such as Pomerol~\cite{Antipov2015}; and for fermions coupled with spins, such as H$\Phi$~\cite{Kawamura2017CPC,Ido2024CPC}.

### 2025-06-01 03_edipack2.tex
Amend ad4d7cc630a5fc8fa6d78971c7b7e0a3bb68d447 I forgot 4 indices...
Updated Bibliobraphy with correct naming conventions <Author><Year><JournalAcronym>[a-z]

The interaction part of the impurity Hamiltonian, 
 $\hat{H}^{\mathrm{int}}$ can in principle contain any 
set of two-body operators: 
\begin{equation}
\hat{H}^\mathrm{int}_\mathrm{imp} = \frac{1}{2} \sum_{ijkl} d^{\dagger}_{i}d^{\dagger}_{j}U_{ijkl}d_{l}d_{k}.\label{HintUmat}
\end{equation}
However, we typically 
adopt a generic formulation of the local multi-orbital Hubbard-Kanamori interaction~\cite{Georges2013ARCMP}:
\begin{equation}\label{Hint}
  \begin{split}
    \hat{H}^\mathrm{int}_\mathrm{imp} &=U\sum_{\a}n_{\a\uparrow}n_{\a\downarrow}+U'\sum_{\a\neq \b}n_{\a\uparrow}n_{\b\downarrow}+(U'-J)\sum_{\a<\b,\sigma}n_{\a\sigma}n_{\b\sigma}\\
    &{\phantom =}- J_X\sum_{\a\neq
      \b}d^\dagger_{\a\uparrow}d_{\a\downarrow}d^\dagger_{\b\downarrow}d_{\b\uparrow}+J_P\sum_{\a
      \neq
      \b}d^\dagger_{\a\uparrow}d^\dagger_{\a\downarrow}d_{\b\downarrow}d_{\b\uparrow},\\
\end{split}
\end{equation}
where we introduced the occupation number operator $n_{\alpha\sigma}=d^\dagger_{\alpha\sigma}d_{\alpha\sigma}$.
The first three terms represent the density-density part of the
interaction, where $U$ is the local intra-orbital Coulomb repulsion,
$U'$ the inter-orbital one and $J$ the Hund's coupling~\cite{Werner2008PRL,Werner2009PR,Mravlje2011PRL,Medici2011PRL,Medici2011PRB,Georges2013ARCMP}.  
The last two terms are, respectively, the spin-exchange ($J_X$) and
the pair-hopping ($J_P$).
In the three-orbital case $N_\a=3$ a fully symmetric $SU(3)_\mathrm{orbital}\otimes SU(2)_\mathrm{spin}\otimes
U(1)_\mathrm{charge}$ form of the interaction is obtained by setting $U'=U-2J$ and
$J_X=J_P=J$~\cite{Georges2013ARCMP}. Different choices, preserving part
of the combined symmetry group, can be made for other numbers of orbitals~\cite{Georges2013ARCMP}.

@@

\subsubsection{Electron-Phonon coupling}
Finally, we include a local electron-phonon coupling on the impurity site
described by the Hamiltonian terms: 
\begin{equation}\label{Hph}
  \begin{split}
    \hat{H}_\mathrm{ph}&=\sum_m \omega_{0m} b_m^\dagger b_m,   \\
    % 
    \hat{H}_\mathrm{e-ph} &= \sum_m [ \hat{O}_m - A_m](b_m+b_m^\dagger), \\
\end{split}
\end{equation}
where $m=1,\dots,M$ indexes the number of local phonon modes, and $b_m$
($b_m^\dagger$) are the destruction (creation) operators for a phonon with
frequency $\omega_{0m}$. Each phonon mode is coupled to a bilinear fermionic operator $\hat{O}_m= \sum_{\alpha \beta, \sigma }g^{m}_{\alpha \beta} d^\dagger_{\alpha, \sigma} d_{\beta, \sigma}$ on the impurity, while $A_m$ is a constant acting as a displacement field.  %Indeed, if the expectation value of the bosonic displacement operator $\langle b_q^\dagger + b_q\rangle$ is non-zero, a change of variables from the bosons $b^{(\dagger)}_q$ leads to new effective bosons $\tilde{b}^{(\dagger)}_q = b^{(\dagger)}_q- A_q$ for which the displacement operator has a smaller expectation value (ideally zero if we can impose $A_m = \langle \hat{O}_m\rangle$). 
%
For single-orbital impurities, the relevant case is $\hat{O}_1 = g_1 n_{1d} = g_1 \sum_{\sigma} d^{\dagger}_{1\sigma}d_{1\sigma}$, which defines the Holstein model\cite{Holstein1959APNY}. For two-orbital models we included also the two Jahn-Teller modes\cite{Capone2010ACMP}, for which $\hat{O}_2 = g_2(n_{1d} - n_{2d})$\cite{Scazzola2023PRB} and $\hat{O}_3 = g_3 \sum_{\sigma} (d^{\dagger}_{1\sigma}d_{2\sigma}+ H.c.)$.

For each phonon mode, one has to introduce a cut-off in the phonon number, which has to be chosen according to the value of the electron-phonon coupling\cite{Capone2003PRL,Capone2006PRB} and its interplay with the electron-electron interaction\cite{Capone2004PRL,Capone2004PRLsc,Sangiovanni2005PRB,Paci2005PRL,Sangiovanni2006PRL,Sangiovanni2006PRB_ph,Paci2006PRB}. The larger the number of excited phonons in the ground state, the larger the cutoff. For practical calculations around 20 phonons are sufficient to achieve converged results except for the deep polaronic regime\cite{Capone2003PRL}.
Choosing properly the shift $A_m$, one can reduce the number of excited phonons in the ground state and consequently the required cutoff. 
Although feasible, dealing with more than one phonon mode quickly becomes computationally very demanding, thus we will consider only one mode and we drop the $m$ index in the rest of this work.

@@

\item{} The {\bf nonsu2} case conserves the total
charge $N$ while allowing the spin symmetry group to be broken.
This scenario captures effects such as local spin-orbit coupling
$\vec{L}\cdot\vec{S}$, in-plane spin ordering~\cite{BellomiaKMH} or
in-plane spin-triplet exciton condensation~\cite{Amaricci2023_excitons,Blason}.  
\end{itemize}

@@

The diagonal spin, charge and pair susceptibility terms
$\chi^{S^z}_{\a\a}$, $\chi^N_{\a\a}$ and $\chi^\Delta_{\a\a}$
are constructed using the operators $S^z_\a = \sum_{\s\s'} c^\dagger_{\a\s}
\tau^z_{\s\s'} c_{\a\s'}$, 
$N_\a = \sum_{\s\s'} c^\dagger_{\a\s} \tau^0_{\s\s'} c_{\a\s'}$
and $\Delta_\a = c_{\a\dw}c_{\a\up}$,
where $\tau^{a=0,x,y,z}$ are the Pauli matrices.
Off-diagonal terms are  evaluated using the operators
$(S^z_\a + S^z_\b)$, $(N_\a + N_\b)$ or $(\Delta_\a + \Delta_\b)$. 
The excitonic susceptibilities, $\chi^{\vec{E}}_{\a\b}$, are defined with 
respect to the vector operator $E^i_{\a\b} = \sum_{\s\s'}
c^\dagger_{\a\s}\tau^i_{\s\s'}c_{\b\s'}$, where $i=0$ represents the
spin-singlet exciton \cite{Giuli2023PRB}, and $i=x,y,z$  correspond to the spin-triplet exciton \cite{Amaricci2023_excitons}.

@@

\subsection{Impurity reduced density matrix}\label{sSecRDM}
The latest version of \NAME introduces the calculation of the 
impurity Reduced Density Matrix (iRDM, $\rho^\mathrm{imp}$), 
extending the algorithm initially proposed in 
Ref.~\onlinecite{BellomiaPhD,Bellomia2024PR}, to support the analysis of entanglement 
properties of quantum impurities for any value of {\tt ed\_mode}.

@@

Using \equ{RhoNormal} the iRDM takes the form:
\begin{equation}
  \label{iRDMnormal}
  \begin{aligned}
  \rho^\mathrm{imp} &= \Tr_{{\color{xkcdCoral}b_\up} {\color{xkcdAzure}b_\dw}}{\rho} = 
  \sum_{{\color{xkcdCoral} b_\up}=1}^{D_{b_\up}}
  \sum_{{\color{xkcdAzure} b_\dw}=1}^{D_{b_\dw}}
  \bra{{\color{xkcdCoral}b_\up}}\otimes\bra{{\color{xkcdAzure}b_\dw}}
    \rho
    \ket{{\color{xkcdAzure}b_\dw}}\otimes\ket{\color{xkcdCoral}{b_\up}}    \cr
    %
    &=
    \sum_{{\color{xkcdCoral} b_\up}=1}^{D_{b_\up}}
    \sum_{{\color{xkcdRaspberry}i_\up}=1}^{D_{i_\up}}\!
    \sum_{{\color{xkcdPumpkin}p_\up}=1}^{D_{p_\up}}\!
    \sum_{{\color{xkcdRaspberry}j_\up}=1}^{D_{j_\up}}\!
    \sum_{{\color{xkcdPumpkin}q_\up}=1}^{D_{q_\up}}\!
    \Bigg(    
    \sum_{{\color{xkcdAzure} b_\dw}=1}^{D_{b_\dw}}
    \sum_{{\color{xkcdPurple}i_\dw}=1}^{D_{i_\dw}}\!
    \sum_{{\color{xkcdTeal}p_\dw}=1}^{D_{p_\dw}}\!
    \sum_{{\color{xkcdPurple}j_\dw}=1}^{D_{j_\dw}}\!
    \sum_{{\color{xkcdTeal}q_\dw}=1}^{D_{q_\dw}}\!
    C_{i,p}\,C_{j,q}\,a_{{\color{xkcdRaspberry}i_\up} {\color{xkcdPumpkin}p_\up} {\color{xkcdPurple}i_\dw} {\color{xkcdTeal}p_\dw}}a^*_{{\color{xkcdRaspberry}j_\up} {\color{xkcdPumpkin}q_\up} {\color{xkcdPurple}j_\dw} {\color{xkcdTeal}q_\dw}} \cr
    %
    &\qquad    
    \langle {\color{xkcdCoral}b_\up}| {\color{xkcdPumpkin}p_\up}\rangle| {\color{xkcdRaspberry}i_\up}\rangle\langle {\color{xkcdRaspberry}j_\up} |\langle {\color{xkcdPumpkin}q_\up}| {\color{xkcdCoral}b_\up}\rangle   \otimes \langle {\color{xkcdAzure}b_\dw}| {\color{xkcdTeal}p_\dw} \rangle|{\color{xkcdPurple}i_\dw}\rangle \langle {\color{xkcdPurple}j_\dw}  |\langle {\color{xkcdTeal}q_\dw}| {\color{xkcdAzure}b_\dw}\rangle \Bigg)
    \cr
&=
    \sum_{i_\up=1}^{D_{i_\up}}
    \sum_{j_\up=1}^{D_{j_\up}}
    \sum_{i_\dw=1}^{D_{i_\dw}}
    \sum_{j_\dw=1}^{D_{j_\dw}}
    \underbrace{\left(
    \sum_{{\color{xkcdCoral} b_\up}=1}^{D_{b_\up}}
    \sum_{{\color{xkcdAzure} b_\dw}=1}^{D_{b_\dw}}
    a_{{\color{xkcdRaspberry}i_\up} {\color{xkcdCoral}b_\up} {\color{xkcdPurple}i_\dw} {\color{xkcdAzure}b_\dw}}a^*_{{\color{xkcdRaspberry}j_\up} {\color{xkcdCoral}b_\up} {\color{xkcdPurple}j_\dw} {\color{xkcdAzure}b_\dw}}
    \right)}_{\rho^\mathrm{imp}_{{\color{xkcdRaspberry}i_\up j_\up}} \otimes\, \rho^\mathrm{imp}_{{\color{xkcdPurple}i_\dw j_\dw}} }
    \ket{{\color{xkcdRaspberry}i_\up}}\bra{{\color{xkcdRaspberry}j_\up}}\otimes \ket{{\color{xkcdPurple}i_\dw}}\bra{{\color{xkcdPurple}j_\dw}},
  \end{aligned}
\end{equation}

@@

Several algorithms have been proposed for this optimization 
step~\cite{Garcia2004PRL,Taranto2012PRB,Mejuto_Bath_ASCI-DMFT}, each with strengths suited 
to different physical contexts. To maintain flexibility in \NAME, 
we keep the optimization part independent 
from the core impurity solver. However, we also include a fully 
integrated optimization routine based on the conjugate gradient (CG) 
minimization of the cost function
\begin{equation}
\chi = \sum_{n=1}^{L_\mathrm{fit}} 
\frac{1}{W_n} \left\|X(i\omega_n) - 
X^\mathrm{QIM}(i\omega_n; \{V, h\}) \right\|_q,
\label{eq:chiq}
\end{equation}
where the $q$-norm is a suitably chosen distance metric in the 
matrix function space. Here, $X_{\a\b} = {\GG_{0}}_{\a\b\s\s'}$ or 
$\Theta_{\a\b\s\s'}$ are the user-supplied local functions, while 
$X_{\a\b}^\mathrm{QIM} = G^0_{\a\b\s\s'}$ or 
$\Delta_{\a\b\s\s'}$ are the corresponding quantities for the quantum 
impurity model, see \secu{sSecFunc}.

While different optimization methods have been developed for 
truncated algorithms, e.g. sCI~\cite{Mejuto_Bath_ASCI-DMFT} or DMRG~\cite{Bauernfeind2017PRX}, 
which handle systems with a 
larger number of bath levels, the CG minimization approach has proven 
both efficient and flexible for the small to moderate bath sizes 
typical in ED solvers.

>>>>

The interaction part of the impurity Hamiltonian, 
 $\hat{H}^{\mathrm{int}}$ can in principle contain any 
set of two-body operators: 
\begin{equation}
\hat{H}^\mathrm{int}_\mathrm{imp} = \frac{1}{2} \sum_{ijkl} d^{\dagger}_{i}d^{\dagger}_{j}U_{ijkl}d_{l}d_{k}.\label{HintUmat}
\end{equation}
However, we typically 
adopt a generic formulation of the local multi-orbital Hubbard-Kanamori interaction~\cite{Georges2013ARCMP}:
\begin{equation}\label{Hint}
  \begin{split}
    \hat{H}^\mathrm{int}_\mathrm{imp} &=U\sum_{\a}n_{\a\uparrow}n_{\a\downarrow}+U'\sum_{\a\neq \b}n_{\a\uparrow}n_{\b\downarrow}+(U'-J)\sum_{\a<\b,\sigma}n_{\a\sigma}n_{\b\sigma}\\
    &{\phantom =}- J_X\sum_{\a\neq
      \b}d^\dagger_{\a\uparrow}d_{\a\downarrow}d^\dagger_{\b\downarrow}d_{\b\uparrow}+J_P\sum_{\a
      \neq
      \b}d^\dagger_{\a\uparrow}d^\dagger_{\a\downarrow}d_{\b\downarrow}d_{\b\uparrow},\\
\end{split}
\end{equation}
where we introduced the occupation number operator $n_{\alpha\sigma}=d^\dagger_{\alpha\sigma}d_{\alpha\sigma}$.
The first three terms represent the density-density part of the
interaction, where $U$ is the local intra-orbital Coulomb repulsion,
$U'$ the inter-orbital one and $J$ the Hund's coupling~\cite{Werner2008PRL,Werner2009PRB,Mravlje2011PRL,Medici2011PRL,Medici2011PRB,Georges2013ARCMP}.  
The last two terms are, respectively, the spin-exchange ($J_X$) and
the pair-hopping ($J_P$).
In the three-orbital case $N_\a=3$ a fully symmetric $SU(3)_\mathrm{orbital}\otimes SU(2)_\mathrm{spin}\otimes
U(1)_\mathrm{charge}$ form of the interaction is obtained by setting $U'=U-2J$ and
$J_X=J_P=J$~\cite{Georges2013ARCMP}. Different choices, preserving part
of the combined symmetry group, can be made for other numbers of orbitals~\cite{Georges2013ARCMP}.

@@

\subsubsection{Electron-Phonon coupling}
Finally, we include a local electron-phonon coupling on the impurity site
described by the Hamiltonian terms: 
\begin{equation}\label{Hph}
  \begin{split}
    \hat{H}_\mathrm{ph}&=\sum_m \omega_{0m} b_m^\dagger b_m,   \\
    % 
    \hat{H}_\mathrm{e-ph} &= \sum_m [ \hat{O}_m - A_m](b_m+b_m^\dagger), \\
\end{split}
\end{equation}
where $m=1,\dots,M$ indexes the number of local phonon modes, and $b_m$
($b_m^\dagger$) are the destruction (creation) operators for a phonon with
frequency $\omega_{0m}$. Each phonon mode is coupled to a bilinear fermionic operator $\hat{O}_m= \sum_{\alpha \beta, \sigma }g^{m}_{\alpha \beta} d^\dagger_{\alpha, \sigma} d_{\beta, \sigma}$ on the impurity, while $A_m$ is a constant acting as a displacement field.  %Indeed, if the expectation value of the bosonic displacement operator $\langle b_q^\dagger + b_q\rangle$ is non-zero, a change of variables from the bosons $b^{(\dagger)}_q$ leads to new effective bosons $\tilde{b}^{(\dagger)}_q = b^{(\dagger)}_q- A_q$ for which the displacement operator has a smaller expectation value (ideally zero if we can impose $A_m = \langle \hat{O}_m\rangle$). 
%
For single-orbital impurities, the relevant case is $\hat{O}_1 = g_1 n_{1d} = g_1 \sum_{\sigma} d^{\dagger}_{1\sigma}d_{1\sigma}$, which defines the Holstein model~\cite{Holstein1959APNY}. For two-orbital models we included also the two Jahn-Teller modes~\cite{Capone2010AICMP}, for which $\hat{O}_2 = g_2(n_{1d} - n_{2d})$~\cite{Scazzola2023PRB} and $\hat{O}_3 = g_3 \sum_{\sigma} (d^{\dagger}_{1\sigma}d_{2\sigma}+ H.c.)$.

For each phonon mode, one has to introduce a cut-off in the phonon number, which has to be chosen according to the value of the electron-phonon coupling~\cite{Capone2003PRL,Capone2006PRB} and its interplay with the electron-electron interaction~\cite{Capone2004PRL,Capone2004PRLsc,Sangiovanni2005PRL,Paci2005PRL,Sangiovanni2006PRL,Sangiovanni2006PRBa,Paci2006PRB}. The larger the number of excited phonons in the ground state, the larger the cutoff. For practical calculations around 20 phonons are sufficient to achieve converged results except for the deep polaronic regime~\cite{Capone2003PRL}.
Choosing properly the shift $A_m$, one can reduce the number of excited phonons in the ground state and consequently the required cutoff. 
Although feasible, dealing with more than one phonon mode quickly becomes computationally very demanding, thus we will consider only one mode and we drop the $m$ index in the rest of this work.

@@

\item{} The {\bf nonsu2} case conserves the total
charge $N$ while allowing the spin symmetry group to be broken.
This scenario captures effects such as local spin-orbit coupling
$\vec{L}\cdot\vec{S}$, in-plane spin ordering~\cite{BellomiaKMH} or
in-plane spin-triplet exciton condensation~\cite{Amaricci2023PRB,Blason2020PRB}.  
\end{itemize}

@@

The diagonal spin, charge and pair susceptibility terms
$\chi^{S^z}_{\a\a}$, $\chi^N_{\a\a}$ and $\chi^\Delta_{\a\a}$
are constructed using the operators $S^z_\a = \sum_{\s\s'} c^\dagger_{\a\s}
\tau^z_{\s\s'} c_{\a\s'}$, 
$N_\a = \sum_{\s\s'} c^\dagger_{\a\s} \tau^0_{\s\s'} c_{\a\s'}$
and $\Delta_\a = c_{\a\dw}c_{\a\up}$,
where $\tau^{a=0,x,y,z}$ are the Pauli matrices.
Off-diagonal terms are  evaluated using the operators
$(S^z_\a + S^z_\b)$, $(N_\a + N_\b)$ or $(\Delta_\a + \Delta_\b)$. 
The excitonic susceptibilities, $\chi^{\vec{E}}_{\a\b}$, are defined with 
respect to the vector operator $E^i_{\a\b} = \sum_{\s\s'}
c^\dagger_{\a\s}\tau^i_{\s\s'}c_{\b\s'}$, where $i=0$ represents the
spin-singlet exciton \cite{Giuli2023PRB}, and $i=x,y,z$  correspond to the spin-triplet exciton \cite{Amaricci2023PRB}.

@@

\subsection{Impurity reduced density matrix}\label{sSecRDM}
The latest version of \NAME introduces the calculation of the 
impurity Reduced Density Matrix (iRDM, $\rho^\mathrm{imp}$), 
extending the algorithm initially proposed in 
Ref.~\cite{BellomiaPhD,Bellomia2024PRB}, to support the analysis of entanglement 
properties of quantum impurities for any value of {\tt ed\_mode}.

@@

Using \equ{RhoNormal} the iRDM takes the form:
\begin{equation}
  \label{iRDMnormal}
  \begin{aligned}
  \rho^\mathrm{imp} &= \Tr_{{\color{xkcdCoral}b_\up} {\color{xkcdAzure}b_\dw}}{\rho} = 
  \sum_{{\color{xkcdCoral} b_\up}=1}^{D_{b_\up}}
  \sum_{{\color{xkcdAzure} b_\dw}=1}^{D_{b_\dw}}
  \bra{{\color{xkcdCoral}b_\up}}\otimes\bra{{\color{xkcdAzure}b_\dw}}
    \rho
    \ket{{\color{xkcdAzure}b_\dw}}\otimes\ket{\color{xkcdCoral}{b_\up}}    \cr
    %
    &=
    \sum_{{\color{xkcdCoral} b_\up}=1}^{D_{b_\up}}
    \sum_{{\color{xkcdRaspberry}i_\up}=1}^{D_{i_\up}}\!
    \sum_{{\color{xkcdPumpkin}p_\up}=1}^{D_{p_\up}}\!
    \sum_{{\color{xkcdRaspberry}j_\up}=1}^{D_{j_\up}}\!
    \sum_{{\color{xkcdPumpkin}q_\up}=1}^{D_{q_\up}}\!
    \Bigg(    
    \sum_{{\color{xkcdAzure} b_\dw}=1}^{D_{b_\dw}}
    \sum_{{\color{xkcdPurple}i_\dw}=1}^{D_{i_\dw}}\!
    \sum_{{\color{xkcdTeal}p_\dw}=1}^{D_{p_\dw}}\!
    \sum_{{\color{xkcdPurple}j_\dw}=1}^{D_{j_\dw}}\!
    \sum_{{\color{xkcdTeal}q_\dw}=1}^{D_{q_\dw}}\!
    C_{i,p}\,C_{j,q}\,a_{{\color{xkcdRaspberry}i_\up} {\color{xkcdPumpkin}p_\up} {\color{xkcdPurple}i_\dw} {\color{xkcdTeal}p_\dw}}a^*_{{\color{xkcdRaspberry}j_\up} {\color{xkcdPumpkin}q_\up} {\color{xkcdPurple}j_\dw} {\color{xkcdTeal}q_\dw}} \cr
    %
    &\qquad    
    \langle {\color{xkcdCoral}b_\up}| {\color{xkcdPumpkin}p_\up}\rangle| {\color{xkcdRaspberry}i_\up}\rangle\langle {\color{xkcdRaspberry}j_\up} |\langle {\color{xkcdPumpkin}q_\up}| {\color{xkcdCoral}b_\up}\rangle   \otimes \langle {\color{xkcdAzure}b_\dw}| {\color{xkcdTeal}p_\dw} \rangle|{\color{xkcdPurple}i_\dw}\rangle \langle {\color{xkcdPurple}j_\dw}  |\langle {\color{xkcdTeal}q_\dw}| {\color{xkcdAzure}b_\dw}\rangle \Bigg)
    \cr
&=
    \sum_{{\color{xkcdRaspberry}i_\up}=1}^{D_{i_\up}}
    \sum_{{\color{xkcdRaspberry}j_\up}=1}^{D_{j_\up}}
    \sum_{{\color{xkcdPurple}i_\dw}=1}^{D_{i_\dw}}
    \sum_{{\color{xkcdPurple}j_\dw}=1}^{D_{j_\dw}}
    \underbrace{\left(
    \sum_{{\color{xkcdCoral} b_\up}=1}^{D_{b_\up}}
    \sum_{{\color{xkcdAzure} b_\dw}=1}^{D_{b_\dw}}
    a_{{\color{xkcdRaspberry}i_\up} {\color{xkcdCoral}b_\up} {\color{xkcdPurple}i_\dw} {\color{xkcdAzure}b_\dw}}a^*_{{\color{xkcdRaspberry}j_\up} {\color{xkcdCoral}b_\up} {\color{xkcdPurple}j_\dw} {\color{xkcdAzure}b_\dw}}
    \right)}_{\rho^\mathrm{imp}_{{\color{xkcdRaspberry}i_\up j_\up}} \otimes\, \rho^\mathrm{imp}_{{\color{xkcdPurple}i_\dw j_\dw}} }
    \ket{{\color{xkcdRaspberry}i_\up}}\bra{{\color{xkcdRaspberry}j_\up}}\otimes \ket{{\color{xkcdPurple}i_\dw}}\bra{{\color{xkcdPurple}j_\dw}},
  \end{aligned}
\end{equation}

@@

Several algorithms have been proposed for this optimization 
step~\cite{Garcia2004PRL,Taranto2012PRB,Mejuto-Zaera2020PRB}, each with strengths suited 
to different physical contexts. To maintain flexibility in \NAME, 
we keep the optimization part independent 
from the core impurity solver. However, we also include a fully 
integrated optimization routine based on the conjugate gradient (CG) 
minimization of the cost function
\begin{equation}
\chi = \sum_{n=1}^{L_\mathrm{fit}} 
\frac{1}{W_n} \left\|X(i\omega_n) - 
X^\mathrm{QIM}(i\omega_n; \{V, h\}) \right\|_q,
\label{eq:chiq}
\end{equation}
where the $q$-norm is a suitably chosen distance metric in the 
matrix function space. Here, $X_{\a\b} = {\GG_{0}}_{\a\b\s\s'}$ or 
$\Theta_{\a\b\s\s'}$ are the user-supplied local functions, while 
$X_{\a\b}^\mathrm{QIM} = G^0_{\a\b\s\s'}$ or 
$\Delta_{\a\b\s\s'}$ are the corresponding quantities for the quantum 
impurity model, see \secu{sSecFunc}.

While different optimization methods have been developed for 
truncated algorithms, e.g. sCI~\cite{Mejuto-Zaera2020PRB} or DMRG~\cite{Bauernfeind2017PRX}, 
which handle systems with a 
larger number of bath levels, the CG minimization approach has proven 
both efficient and flexible for the small to moderate bath sizes 
typical in ED solvers.

### 2025-06-01 04_cbinding.tex
Updated Bibliobraphy with correct naming conventions <Author><Year><JournalAcronym>[a-z]

\section{Interoperability}\label{SecInterop}
The recent growing availability of state-of-the-art software dedicated
to the solution of quantum impurity problems using different methods \cite{Bulla2008RMP,Parcollet2015CPC,Seth2016CPC,Bauernfeind2017PRX,Ganahl2015PRB,Wallerberger2019CPC,Mejuto_Bath_ASCI-DMFT}
poses a challenge to test accuracy and reliability of the
results.
As such, software packages are expected to develop a higher level of interoperability, i.e. the capability to operate with other software, possibly written in different programming languages.
Modern Fortran, which is the language of choice for \NAME, since many
years supports the standardized generation of procedures and
variables that are interoperable with C.
Here we describe the implementation of an interoperability layer aiming at developing APIs for other languages as well as 
integrating \NAME in complex scientific frameworks, e.g. TRIQS~\cite{Parcollet2015CPC} or W2Dynamics~\cite{Wallerberger2019CPC}.

>>>>

\section{Interoperability}\label{SecInterop}
The recent growing availability of state-of-the-art software dedicated
to the solution of quantum impurity problems using different methods \cite{Bulla2008RMP,Parcollet2015CPC,Seth2016CPC,Bauernfeind2017PRX,Ganahl2015PRB,Wallerberger2019CPC,Mejuto-Zaera2020PRB}
poses a challenge to test accuracy and reliability of the
results.
As such, software packages are expected to develop a higher level of interoperability, i.e. the capability to operate with other software, possibly written in different programming languages.
Modern Fortran, which is the language of choice for \NAME, since many
years supports the standardized generation of procedures and
variables that are interoperable with C.
Here we describe the implementation of an interoperability layer aiming at developing APIs for other languages as well as 
integrating \NAME in complex scientific frameworks, e.g. TRIQS~\cite{Parcollet2015CPC} or W2Dynamics~\cite{Wallerberger2019CPC}.
